### 2023-06-20 python_excel_ite.tex
found strategy for code samples using tcolorbox and minted

\usepackage{hyperref}
\usepackage{listings}
\usepackage{xcolor}

% User added usepackage commands from Jupyter notebook preamble
\usepackage{tcolorbox}
%\usepackage{graphicx}
%\usepackage{float}
%\usepackage{xcolor} % Allow colors to be defined
\usepackage{enumerate} % Needed for markdown enumerations to work
\usepackage{geometry} % Used to adjust the document margins
%\usepackage{amsmath} % Equations
%\usepackage{amssymb} % Equations
\usepackage{textcomp} % defines textquotesingle
% Hack from http://tex.stackexchange.com/a/47451/13684:
\AtBeginDocument{%
	\def\PYZsq{\textquotesingle}% Upright quotes in Pygmentized code
}
\usepackage{upquote} % Upright quotes for verbatim code
\usepackage{eurosym} % defines \euro

\usepackage{fancyvrb} % verbatim replacement that allows latex

% Private macros for Jupyter notebook styling

% Colors for the hyperref package
\definecolor{urlcolor}{rgb}{0,.145,.698}
\definecolor{linkcolor}{rgb}{.71,0.21,0.01}
\definecolor{citecolor}{rgb}{.12,.54,.11}

% ANSI colors
\definecolor{ansi-black}{HTML}{3E424D}
\definecolor{ansi-black-intense}{HTML}{282C36}
\definecolor{ansi-red}{HTML}{E75C58}
\definecolor{ansi-red-intense}{HTML}{B22B31}
\definecolor{ansi-green}{HTML}{00A250}
\definecolor{ansi-green-intense}{HTML}{007427}
\definecolor{ansi-yellow}{HTML}{DDB62B}
\definecolor{ansi-yellow-intense}{HTML}{B27D12}
\definecolor{ansi-blue}{HTML}{208FFB}
\definecolor{ansi-blue-intense}{HTML}{0065CA}
\definecolor{ansi-magenta}{HTML}{D160C4}
\definecolor{ansi-magenta-intense}{HTML}{A03196}
\definecolor{ansi-cyan}{HTML}{60C6C8}
\definecolor{ansi-cyan-intense}{HTML}{258F8F}
\definecolor{ansi-white}{HTML}{C5C1B4}
\definecolor{ansi-white-intense}{HTML}{A1A6B2}
\definecolor{ansi-default-inverse-fg}{HTML}{FFFFFF}
\definecolor{ansi-default-inverse-bg}{HTML}{000000}

% Pygments definitions
\makeatletter
\def\PY@reset{\let\PY@it=\relax \let\PY@bf=\relax%
	\let\PY@ul=\relax \let\PY@tc=\relax%
	\let\PY@bc=\relax \let\PY@ff=\relax}
\def\PY@tok#1{\csname PY@tok@#1\endcsname}
\def\PY@toks#1+{\ifx\relax#1\empty\else%
	\PY@tok{#1}\expandafter\PY@toks\fi}
\def\PY@do#1{\PY@bc{\PY@tc{\PY@ul{%
				\PY@it{\PY@bf{\PY@ff{#1}}}}}}}
\def\PY#1#2{\PY@reset\PY@toks#1+\relax+\PY@do{#2}}

\@namedef{PY@tok@w}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.73,0.73}{##1}}}
\@namedef{PY@tok@c}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cp}{\def\PY@tc##1{\textcolor[rgb]{0.61,0.40,0.00}{##1}}}
\@namedef{PY@tok@k}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kp}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kt}{\def\PY@tc##1{\textcolor[rgb]{0.69,0.00,0.25}{##1}}}
\@namedef{PY@tok@o}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@ow}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\@namedef{PY@tok@nb}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@nf}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@nc}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@nn}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@ne}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.80,0.25,0.22}{##1}}}
\@namedef{PY@tok@nv}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@no}{\def\PY@tc##1{\textcolor[rgb]{0.53,0.00,0.00}{##1}}}
\@namedef{PY@tok@nl}{\def\PY@tc##1{\textcolor[rgb]{0.46,0.46,0.00}{##1}}}
\@namedef{PY@tok@ni}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.44,0.44,0.44}{##1}}}
\@namedef{PY@tok@na}{\def\PY@tc##1{\textcolor[rgb]{0.41,0.47,0.13}{##1}}}
\@namedef{PY@tok@nt}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@nd}{\def\PY@tc##1{\textcolor[rgb]{0.67,0.13,1.00}{##1}}}
\@namedef{PY@tok@s}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sd}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@si}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.64,0.35,0.47}{##1}}}
\@namedef{PY@tok@se}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.67,0.36,0.12}{##1}}}
\@namedef{PY@tok@sr}{\def\PY@tc##1{\textcolor[rgb]{0.64,0.35,0.47}{##1}}}
\@namedef{PY@tok@ss}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@sx}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@m}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@gh}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\@namedef{PY@tok@gu}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.50,0.00,0.50}{##1}}}
\@namedef{PY@tok@gd}{\def\PY@tc##1{\textcolor[rgb]{0.63,0.00,0.00}{##1}}}
\@namedef{PY@tok@gi}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.52,0.00}{##1}}}
\@namedef{PY@tok@gr}{\def\PY@tc##1{\textcolor[rgb]{0.89,0.00,0.00}{##1}}}
\@namedef{PY@tok@ge}{\let\PY@it=\textit}
\@namedef{PY@tok@gs}{\let\PY@bf=\textbf}
\@namedef{PY@tok@gp}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,0.50}{##1}}}
\@namedef{PY@tok@go}{\def\PY@tc##1{\textcolor[rgb]{0.44,0.44,0.44}{##1}}}
\@namedef{PY@tok@gt}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.27,0.87}{##1}}}
\@namedef{PY@tok@err}{\def\PY@bc##1{{\setlength{\fboxsep}{\string -\fboxrule}\fcolorbox[rgb]{1.00,0.00,0.00}{1,1,1}{\strut ##1}}}}
\@namedef{PY@tok@kc}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kd}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kn}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@kr}{\let\PY@bf=\textbf\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@bp}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.50,0.00}{##1}}}
\@namedef{PY@tok@fm}{\def\PY@tc##1{\textcolor[rgb]{0.00,0.00,1.00}{##1}}}
\@namedef{PY@tok@vc}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vg}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vi}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@vm}{\def\PY@tc##1{\textcolor[rgb]{0.10,0.09,0.49}{##1}}}
\@namedef{PY@tok@sa}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sb}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sc}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@dl}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@s2}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@sh}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@s1}{\def\PY@tc##1{\textcolor[rgb]{0.73,0.13,0.13}{##1}}}
\@namedef{PY@tok@mb}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mf}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mh}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mi}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@il}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@mo}{\def\PY@tc##1{\textcolor[rgb]{0.40,0.40,0.40}{##1}}}
\@namedef{PY@tok@ch}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cm}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cpf}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@c1}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}
\@namedef{PY@tok@cs}{\let\PY@it=\textit\def\PY@tc##1{\textcolor[rgb]{0.24,0.48,0.48}{##1}}}

\def\PYZbs{\char`\\}
\def\PYZus{\char`\_}
\def\PYZob{\char`\{}
\def\PYZcb{\char`\}}
\def\PYZca{\char`\^}
\def\PYZam{\char`\&}
\def\PYZlt{\char`\<}
\def\PYZgt{\char`\>}
\def\PYZsh{\char`\#}
\def\PYZpc{\char`\%}
\def\PYZdl{\char`\$}
\def\PYZhy{\char`\-}
\def\PYZsq{\char`\'}
\def\PYZdq{\char`\"}
\def\PYZti{\char`\~}
% for compatibility with earlier versions
\def\PYZat{@}
\def\PYZlb{[}
\def\PYZrb{]}
\makeatother

    % Define a nice break command that doesn't care if a line doesn't already
% exist.
\def\br{\hspace*{\fill} \\* }

% For linebreaks inside Verbatim environment from package fancyvrb.
\makeatletter
\newbox\Wrappedcontinuationbox
\newbox\Wrappedvisiblespacebox
\newcommand*\Wrappedvisiblespace {\textcolor{red}{\textvisiblespace}}
\newcommand*\Wrappedcontinuationsymbol {\textcolor{red}{\llap{\tiny$\m@th\hookrightarrow$}}}
\newcommand*\Wrappedcontinuationindent {3ex }
\newcommand*\Wrappedafterbreak {\kern\Wrappedcontinuationindent\copy\Wrappedcontinuationbox}
% Take advantage of the already applied Pygments mark-up to insert
% potential linebreaks for TeX processing.
%        {, <, #, %, $, ' and ": go to next line.
%        _, }, ^, &, >, - and ~: stay at end of broken line.
% Use of \textquotesingle for straight quote.
\newcommand*\Wrappedbreaksatspecials {%
	\def\PYGZus{\discretionary{\char`\_}{\Wrappedafterbreak}{\char`\_}}%
	\def\PYGZob{\discretionary{}{\Wrappedafterbreak\char`\{}{\char`\{}}%
	\def\PYGZcb{\discretionary{\char`\}}{\Wrappedafterbreak}{\char`\}}}%
	\def\PYGZca{\discretionary{\char`\^}{\Wrappedafterbreak}{\char`\^}}%
	\def\PYGZam{\discretionary{\char`\&}{\Wrappedafterbreak}{\char`\&}}%
	\def\PYGZlt{\discretionary{}{\Wrappedafterbreak\char`\<}{\char`\<}}%
	\def\PYGZgt{\discretionary{\char`\>}{\Wrappedafterbreak}{\char`\>}}%
	\def\PYGZsh{\discretionary{}{\Wrappedafterbreak\char`\#}{\char`\#}}%
	\def\PYGZpc{\discretionary{}{\Wrappedafterbreak\char`\%}{\char`\%}}%
	\def\PYGZdl{\discretionary{}{\Wrappedafterbreak\char`\$}{\char`\$}}%
	\def\PYGZhy{\discretionary{\char`\-}{\Wrappedafterbreak}{\char`\-}}%
	\def\PYGZsq{\discretionary{}{\Wrappedafterbreak\textquotesingle}{\textquotesingle}}%
	\def\PYGZdq{\discretionary{}{\Wrappedafterbreak\char`\"}{\char`\"}}%
	\def\PYGZti{\discretionary{\char`\~}{\Wrappedafterbreak}{\char`\~}}%
}
% Some characters . , ; ? ! / are not pygmentized.
% This macro makes them "active" and they will insert potential linebreaks
\newcommand*\Wrappedbreaksatpunct {%
	\lccode`\~`\.\lowercase{\def~}{\discretionary{\hbox{\char`\.}}{\Wrappedafterbreak}{\hbox{\char`\.}}}%
	\lccode`\~`\,\lowercase{\def~}{\discretionary{\hbox{\char`\,}}{\Wrappedafterbreak}{\hbox{\char`\,}}}%
	\lccode`\~`\;\lowercase{\def~}{\discretionary{\hbox{\char`\;}}{\Wrappedafterbreak}{\hbox{\char`\;}}}%
	\lccode`\~`\:\lowercase{\def~}{\discretionary{\hbox{\char`\:}}{\Wrappedafterbreak}{\hbox{\char`\:}}}%
	\lccode`\~`\?\lowercase{\def~}{\discretionary{\hbox{\char`\?}}{\Wrappedafterbreak}{\hbox{\char`\?}}}%
	\lccode`\~`\!\lowercase{\def~}{\discretionary{\hbox{\char`\!}}{\Wrappedafterbreak}{\hbox{\char`\!}}}%
	\lccode`\~`\/\lowercase{\def~}{\discretionary{\hbox{\char`\/}}{\Wrappedafterbreak}{\hbox{\char`\/}}}%
	\catcode`\.\active
	\catcode`\,\active
	\catcode`\;\active
	\catcode`\:\active
	\catcode`\?\active
	\catcode`\!\active
	\catcode`\/\active
	\lccode`\~`\~
}
\makeatother

\let\OriginalVerbatim=\Verbatim
\makeatletter
\renewcommand{\Verbatim}[1][1]{%
	%\parskip\z@skip
	\sbox\Wrappedcontinuationbox {\Wrappedcontinuationsymbol}%
	\sbox\Wrappedvisiblespacebox {\FV@SetupFont\Wrappedvisiblespace}%
	\def\FancyVerbFormatLine ##1{\hsize\linewidth
		\vtop{\raggedright\hyphenpenalty\z@\exhyphenpenalty\z@
			\doublehyphendemerits\z@\finalhyphendemerits\z@
			\strut ##1\strut}%
	}%
	% If the linebreak is at a space, the latter will be displayed as visible
	% space at end of first line, and a continuation symbol starts next line.
	% Stretch/shrink are however usually zero for typewriter font.
	\def\FV@Space {%
		\nobreak\hskip\z@ plus\fontdimen3\font minus\fontdimen4\font
		\discretionary{\copy\Wrappedvisiblespacebox}{\Wrappedafterbreak}
		{\kern\fontdimen2\font}%
	}%

	% Allow breaks at special characters using \PYG... macros.
	\Wrappedbreaksatspecials
	% Breaks at punctuation characters . , ; ? ! and / need catcode=\active
	\OriginalVerbatim[#1,codes*=\Wrappedbreaksatpunct]%
}
\makeatother

% Exact colors from NB
\definecolor{incolor}{HTML}{303F9F}
\definecolor{outcolor}{HTML}{D84315}
\definecolor{cellborder}{HTML}{CFCFCF}
\definecolor{cellbackground}{HTML}{F7F7F7}

% prompt
\makeatletter
\newcommand{\boxspacing}{\kern\kvtcb@left@rule\kern\kvtcb@boxsep}
\makeatother
\newcommand{\prompt}[4]{
	{\ttfamily\llap{{\color{#2}[#3]:\hspace{3pt}#4}}\vspace{-\baselineskip}}
}

% Prevent overflowing lines due to hard-to-break entities
\sloppy
% Setup hyperref package
\hypersetup{
	breaklinks=true,  % so long urls are correctly broken across lines
	colorlinks=true,
	urlcolor=urlcolor,
	linkcolor=linkcolor,
	citecolor=citecolor,
}
% Slightly bigger margins than the latex defaults

\geometry{verbose,tmargin=1in,bmargin=1in,lmargin=1in,rmargin=1in}

@@

\definecolor{LightGray}{gray}{0.9}
\definecolor{codegreen}{rgb}{0,0.6,0}
\definecolor{codegray}{rgb}{0.5,0.5,0.5}
\definecolor{codepurple}{rgb}{0.58,0,0.82}
\definecolor{backcolour}{rgb}{0.95,0.95,0.92}
\lstdefinestyle{mystyle}{
	backgroundcolor=\color{LightGray},   
    commentstyle=\color{codegreen},
	keywordstyle=\color{magenta},
	numberstyle=\tiny\color{codegreen},
	stringstyle=\color{codepurple},
	basicstyle=\footnotesize\ttfamily,
	breakatwhitespace=false,         
	breaklines=true,                 
	captionpos=b,                    
	keepspaces=true,                 
	numbers=left,                    
	numbersep=5pt,                  
	showspaces=false,                
	showstringspaces=false,
	showtabs=false,                  
	tabsize=2
}

\lstset{style=mystyle}

@@

% The opening part of the what-if notebook has some language for the motivation behind this module.
% TODO - opening should really grab reader
Spreadsheet based modeling wave of the early 2000s. TMS conferences. Ground breaking textbooks such as Ragsdale and W\&A.

@@

% TODO - how should pandas appear in text
Python has continued to make inroads to analytical territory that was formerly dominated by Excel. The widely used Python data analysis library, Pandas, was created by Wes McKinney while working as a quantitative financial analyst. However, Python was mainly used for data wrangling, visualization and predictive modeling using various flavors of regression and tree based models. The blog \href{https://pbpython.com/}{Practical Business Python} written primarily by Chris Moffitt contributed greatly to making Python more accessible to business analytics practitioners through high quality posts that were extremely practical and useful. But, it got me to thinking. What about those things for which Excel is well suited such as building formula based models and doing sensitivity analysis on these models? What would those look like in Python?

@@

The stage is set with an overview of a typical spreadsheet based model that most of the students have seen before.

\begin{quote}
	For example, here's a high level screenshot of a model that I assign for homework in my [MIS 4460/5460 Business Analytics class](http://www.sba.oakland.edu/faculty/isken/courses/mis5460/) (a spreadsheet based modeling class).
	It's a really simple model in which we are selling a single product that we produce. There is a fixed cost to producing the product as well as a variable production cost per unit. We can sell the product for some price and we believe that demand for the product is related to the selling price through a power function. Let's assume for now that we have sufficient capacity to produce to demand and that all inputs are deterministic (we'll deal with simulating uncertainty later in this document).

	The details aren't so important right now as is the overall structure of the model. There's a few key inputs and some pretty straightforward formulas for computing cost, revenue and profit. Notice the 1-way Data Table being used to explore how profit varies for different selling prices. There's a graph driven by the Data Table and some Text Boxes used for annotation and summary interpretative comments. There's a button that launches Goal Seek to find the break even selling price and a 2-way Data Table (not shown) to explore the joint effect of selling price and variable cost. Classic Excel modeling stuff. How might we go about building a similar model using Python?

	What if we wanted to push it a little further and model some of the key inputs with probability distributions to reflect our uncertainty about their values? In the Excel world, we might use add-ins such as @Risk which allow uncertain quantities to be directly modeled with probability distributions. For example, we might have a key input such as the exponent in the power function that relates selling price to demand that is highly uncertain. By modeling it with a probability distribution and then sampling from that distribution many times (essentially by recalcing the spreadsheet) we can generate a bunch of possible values for key outputs (e.g. profit) and use statistics to summarize these outputs using things like histograms and summary stats. Often this type of simulation model is referred to as a *Monte-Carlo* model to suggest repeated sampling from one or more probability distributions within an otherwise pretty static model. If you want to see such models in action, check out my [Simulation Modeling with Excel page](http://www.sba.oakland.edu/faculty/isken/courses/mis5460/simulation.html) from my Business Analytics course. Again, how might we do this with Python?
\end{quote}

@@

With this as motivation, we then introduce a similar modeling problem. The example used throughout the rest of the notebook is based on one in the [spreadsheet modeling textbooks I've used in my classes since 2001](https://host.kelley.iu.edu/albrightbooks/). In both books, they introduce the "Walton Bookstore" problem in the chapter on Monte-Carlo simulation. Here is the basic problem (with a few modifications):

@@

@@

We start with a very simple model that ignores the uncertainty in demand and that is not object oriented. Proceeding much like we would in Excel, we store base input values in variables.

\begin{lstlisting}[language=Python]
# Base inputs
unit_cost = 7.50
selling_price = 10.00
unit_refund = 2.50

@@

# Initial value for order quantity - this is the decision variable
order_quantity = 200
\end{lstlisting}

\begin{tcolorbox}[breakable, size=fbox, boxrule=1pt, pad at break*=1mm,colback=cellbackground, colframe=cellborder]
	%\prompt{In}{incolor}{3}{\boxspacing}
	\begin{Verbatim}[commandchars=\\\{\}]
	\PY{c+c1}{\PYZsh{} Base inputs}
	\PY{n}{unit\PYZus{}cost} \PY{o}{=} \PY{l+m+mf}{7.50}
	\PY{n}{selling\PYZus{}price} \PY{o}{=} \PY{l+m+mf}{10.00}
	\PY{n}{unit\PYZus{}refund} \PY{o}{=} \PY{l+m+mf}{2.50}
	\end{Verbatim}
\end{tcolorbox}

@@

\begin{lstlisting}[language=Python]
order_cost = unit_cost * order_quantity
sales_revenue = ??? * selling_price
refund_revenue = ??? * unit_refund
profit = sales_revenue + refund_revenue - order_cost
\end{lstlisting}

@@

Since order quantity is the key decision variable, we might want to see how profit changes for different order quantities. In Excel, the Data Table tool provides an easy way to do this and is a staple of spreadsheet based management science textbooks. In a Data Table, a range of order quantities can be used as row or column input and one or more output values can be computed. In Python, we can rely on the vectorized behavior of the language \cite{bibid}. A range of order quantities is created as a NumPy array that can be used directly to compute vectors of all of the intermediate and final output variables. Much like Data Tables, vectorized computations avoid having to explicitly iterate, or loop, through a collection of input values.

A natural next step is to do the equivalent of an Excel 2-way Data Table. By creating a profit function that takes all of the base inputs as arguments, we can construct a list comprehension that does what an Excel 2-Way Data Table does. Even better, this actually allows us to do the equivalent of an n-Way Data Table with an arbitrary number of outputs - something Excel does not have. This example provides an effective way to show the power of creating reusable functions and Python's handy list comprehension construct.

\begin{lstlisting}[language=Python]
	def bookstore_profit(unit_cost, selling_price, unit_refund, order_quantity, demand):
	'''
	Compute profit in bookstore model
	'''
		order_cost = unit_cost * order_quantity
		sales_revenue = np.minimum(order_quantity, demand) * selling_price
		refund_revenue = np.maximum(0, order_quantity - demand)
		profit = sales_revenue + refund_revenue - order_cost
		return profit

@@

	# Create data table (as a list of tuples)
	data_table_1 = [(d, oq, bookstore_profit(unit_cost, selling_price, unit_refund, oq, d)) 
	for d in demand_range for oq in order_quantity_range]

@@

\end{lstlisting}

@@

@@

It is not clear whether an object oriented (OO) or a non-OO approach will end up making the most sense for doing spreadsheet type modeling. This uncertainty is made explicit in the notebook and students are led on a bit of a journey of discovery as we explore different software designs for this modeling problem. I purposefully designed the notebooks in this way to show students that the path to a solution is not necessarily linear and that giving yourself the freedom to explore alternatives, many of which will be dead ends, can lead to a rich learning experience. It is also more realistic in the sense that this is how most real problems are solved. It is analogous to the idea that mathematical proofs usually do not reflect the myriad of failed approaches that were tried but that ultimately contributed to the final product.

@@

The EwP module ends with what has become a relatively common use of Python with Excel - automating various Excel data wrangling tasks. Examples include:

>>>>

\usepackage[most]{tcolorbox}
\usepackage{minted}
\tcbuselibrary{minted} % tcolorbox minted library, required to use the "minted" tcb listing engine (this library is not loaded by the option [most])
%\usepackage{minted} % Allows input of raw code, such as Python code
\usepackage[colorlinks]{hyperref} % ALWAYS load this package LAST

@@

@@

% The opening part of the what-if notebook has some language for the motivation behind this module.
% TODO - opening should really grab reader
Spreadsheet based modeling has transformed the teaching of management science in business schools. The late 1990's saw the first editions of game changing textbooks \cite{ } focused on the use of spreadsheets in teaching modeling and management science.  A series of conferences focused on teaching management science (TMS) with spreadsheets started at Dartmouth in 1998 and several presentations from that conference made up the bulk of papers in the first two issues of the INFORMS Transactions on Education journal \cite{bibid}. I attended TMS III at Indiana University and left with numerous ideas that influenced my own spreadsheet based modeling course. The next few decades saw numerous textbooks and teaching papers that prominently featured spreadsheet based modeling.

Despite numerous calls for and predictions of the eradication of spreadsheets from the business world,

Spreadsheet based modeling wave of the early 2000s. TMS conferences. Ground breaking textbooks such as Ragsdale and W\&A.
The first two issues of ITE are paper based on TMS 1 at Dartmouth in 1998. I attended TMS 3 in Bloomington in 2000.

First edition of Ragsdale was 1995 PMS was 1997.

While spreadsheets have certainly changed and expanded in their capabilities (PowerPivot, um...) since the 90's...

Irony of Mgt Sci crisis of 1990's where course was dropped by AACSB and ignored by other business disciplines to an era where analytics has captured the day and now AI threatens even that.

Powell's 2001 paper on the importance of modeling is no less relevant now than it was when published. I still many of his ideas in my spreadsheet based modeling course.

@@

Python has continued to make inroads to analytical territory that was formerly dominated by Excel. The widely used Python data analysis library, Pandas, was created by Wes McKinney while working as a quantitative financial analyst. However, Python was mainly used for data wrangling, visualization and predictive modeling using various flavors of regression and tree based models. The blog \href{https://pbpython.com/}{Practical Business Python} written primarily by Chris Moffitt contributed greatly to making Python more accessible to business analytics practitioners through high quality posts that were extremely practical and useful. But, it got me to thinking. What about those things for which Excel is well suited such as building formula based models and doing sensitivity analysis on these models? What would those look like in Python?

@@

The stage is set with an overview of a typical spreadsheet based model that most of the students have seen before. See Figure \ref{fig:xl_model} for a screenshot of the Excel model.

\begin{tcolorbox}
\begin{quotation}
\textsf{	
	It's a really simple model in which we are selling a single product that we produce. There is a fixed cost to producing the product as well as a variable production cost per unit. We can sell the product for some price and we believe that demand for the product is related to the selling price through a power function. Let's assume for now that we have sufficient capacity to produce to demand and that all inputs are deterministic (we'll deal with simulating uncertainty later in this document).}

	\textsf{The details aren't so important right now as is the overall structure of the model. There's a few key inputs and some pretty straightforward formulas for computing cost, revenue and profit. Notice the 1-way Data Table being used to explore how profit varies for different selling prices. There's a graph driven by the Data Table and some Text Boxes used for annotation and summary interpretative comments. There's a button that launches Goal Seek to find the break even selling price and a 2-way Data Table (not shown) to explore the joint effect of selling price and variable cost. Classic Excel modeling stuff. How might we go about building a similar model using Python? }

	\textsf{What if we wanted to push it a little further and model some of the key inputs with probability distributions to reflect our uncertainty about their values? In the Excel world, we might use add-ins such as @Risk which allow uncertain quantities to be directly modeled with probability distributions. For example, we might have a key input such as the exponent in the power function that relates selling price to demand that is highly uncertain. By modeling it with a probability distribution and then sampling from that distribution many times (essentially by recalcing the spreadsheet) we can generate a bunch of possible values for key outputs (e.g. profit) and use statistics to summarize these outputs using things like histograms and summary stats. Often this type of simulation model is referred to as a Monte-Carlo model to suggest repeated sampling from one or more probability distributions within an otherwise pretty static model. Again, how might we do this with Python?}
\end{quotation}
\end{tcolorbox}

@@

We then introduce a similar modeling problem to use throughout the rest of the notebook. The Walton Bookstore problem appears in the chapter on Monte-Carlo simulation in textbooks that I have used in my spreadsheet modeling course \cite{albrightBusinessAnalyticsData2016,winstonPracticalManagementScience2018}. The (slightly modified) problem is as follows:

@@

The goal is to build a Python based version of this model that will allow us to do sensitivity analysis, find the break even point for demand and analyze the problem using Monte-Carlo simulation.

@@

We start with a very simple model that ignores the uncertainty in demand and that is not object oriented. Proceeding much like we would in Excel, base input values are stored in variables.

\begin{tcolorbox}
\begin{minted}[gobble=0]{python}
# Base inputs
unit_cost = 7.50
selling_price = 10.00
unit_refund = 2.50

@@

# Initial value for order quantity - this is the decision variable
order_quantity = 200
\end{minted}
\end{tcolorbox}

@@

\begin{tcolorbox}
\begin{minted}[gobble=0]{python}
order_cost = unit_cost * order_quantity
sales_revenue = ??? * selling_price
refund_revenue = ??? * unit_refund
profit = sales_revenue + refund_revenue - order_cost
\end{minted}
\end{tcolorbox}

@@

Since order quantity is the key decision variable, we might want to see how profit changes for different order quantities. In Excel, the Data Table tool provides an easy way to do this and is a staple of spreadsheet based management science textbooks. In a Data Table, a range of order quantities can be used as row or column input and one or more output values can be computed. In Python, the vectorized behavior of the language \cite{bibid} provides a simple way to accomplish the same thing. A range of order quantities is created as a NumPy array that can be used directly to compute vectors of all of the intermediate and final output variables. Much like Data Tables, vectorized computations avoid having to explicitly iterate, or loop, through a collection of input values.

A natural next step is to do the equivalent of an Excel 2-way Data Table. By creating a profit function that takes all of the base inputs as arguments, a list comprehension can then be used to generate the equivalent of a 2-way Data Table. Even better, this actually allows us to do the equivalent of an n-way Data Table with an arbitrary number of outputs -- something Excel does not have. This example provides an effective way to show the power of creating reusable functions and Python's handy list comprehension construct.

This code chunk,

\begin{tcolorbox}[left=0mm]
\begin{minted}[gobble=1]{python}
	def bookstore_profit(unit_cost, selling_price, 
	                     unit_refund, order_quantity, demand):
	'''
	Compute profit in bookstore model
	'''
		order_cost = unit_cost * order_quantity
		sales_revenue = np.minimum(order_quantity, demand) * selling_price
		refund_revenue = np.maximum(0, order_quantity - demand)
		profit = sales_revenue + refund_revenue - order_cost
		return profit

@@

	# Create data table (as a list of tuples)
	data_table_1 = [(d, oq, bookstore_profit(
	                 unit_cost, selling_price, unit_refund, oq, d)) 
	for d in demand_range for oq in order_quantity_range]

@@

\end{minted}
\end{tcolorbox}

results in the following output:

@@

\begin{tcolorbox}
	\begin{verbatim}
	   Demand  OrderQuantity  Profit
	      50             50   125.0
	      50             75   -37.5
	      50            100  -200.0
	      50            125  -362.5
	      50            150  -525.0
	      ...
	     300            275   687.5
	     300            300   750.0
\end{verbatim}	
\end{tcolorbox}

@@

It is not clear whether this non-object oriented approach will end up making the most sense for doing spreadsheet type modeling in Python. This uncertainty is made explicit in the notebook and students are led on a bit of a journey of discovery as we explore different software designs for this modeling problem. I purposefully designed the notebooks in this way to show students that the path to a solution is not necessarily linear and that giving yourself the freedom to explore alternatives, many of which will be dead ends, can lead to a rich learning experience. It is also more realistic in the sense that this is how most real problems are solved. It is analogous to the idea that mathematical proofs usually do not reflect the myriad of failed approaches that were tried but that ultimately contributed to the final product.

@@

The EwP module ends with what has become a relatively common use of Python with Excel -- automating various Excel data wrangling tasks. Examples include:
